Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-01-09 paper.tex
little ending

Figure~\ref{fig:PF_plot_ave} shows the plot of the charge mobility one logarithmic $y$-axis as a function of $\sqrt{F}$ to reveal the electric field dependence of the type $\mu(F)=\mu_0 \exp (\beta \sqrt{F})$ as predicted by Poole and Frenkel~\cite{frenkel_prebreakdown_1938}. We show the explicit results for the six chosen \ahfx values together with the confidence interval estimate from the uncertainty quantification via Monte-Carlo sampling.

\bjoern{STOP}{HERE}

%As the electric increase from $|\vec{F}|=4 \cdot 10^7 \unit{V/m}$
%$|\vec{F}|=9 \cdot 10^7 \unit{V/m}$, the
%range of the 90\% confidence interval \bjoern{TO CHECK}{above and below it is 99\%!!} where $\log_{10} \mu_\text{PF}$ lies
%estimated from the MC sample decrease from 0.90 to 0.69.
%So the electric field results in a narrower range of $\mu_\text{PF}$ distribution.

This interval suggests that if the uncertainties from the parameters are represented by the maximum likelihood distribution, the Poole–Frenkel plot from $\alpha=0$ has less 1\% chance to happen and thus is very likely.

\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
  \caption{\label{tab:PF_parameter}%
  Poole-Frenkel parameters $\mu_0$ (in $\unit[]{cm^2/(Vs)}$) and $\beta$ (in $\unit[]{\sqrt{cm/V}}$) of the multiscale modeled MADN, calculated by the six different HFX values. 
  }
  \begin{ruledtabular}
    \begin{tabular}{c c c c c}
    $\alpha$ & & $\mu_0$  & & $\beta$ \\
      \hline
    0 & & $4.0 \cdot 10^{-3}$ & & $1.0 \cdot 10^{-3}$ \\
    0.05 & & $2.1 \cdot 10^{-3}$ & & $9.3 \cdot 10^{-4}$ \\
    0.10 & & $1.0 \cdot 10^{-3}$ & & $1.5 \cdot 10^{-3}$ \\
    0.15 & & $8.0 \cdot 10^{-4}$ & & $1.6 \cdot 10^{-3}$ \\
    0.20 & & $9.3 \cdot 10^{-4}$ & & $1.3 \cdot 10^{-3}$ \\
    0.25 & & $2.6 \cdot 10^{-4}$ & & $1.8 \cdot 10^{-3}$ \\
      \end{tabular}
  \end{ruledtabular}
  \end{table}

The extracted Poole–Frenkel paratermeter calculated from the six $\alpha$ values are summarized in Table \ref{tab:PF_parameter}. 
Excluding the data of $\alpha=0$, the extracted zero-field mobility $\mu_0$ has a range from $2.6 \cdot 10^{-4}$ to $2.1 \cdot 10^{-3}$, and the field effect constant $\beta$ range from $9.3 \cdot 10^{-4}$ to $1.8 \cdot 10^{-3}$.
So $\beta$ is less sensitive to the multiscale model parameter $\alpha$ compared the zero-field mobility.

>>>>

\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
  \caption{\label{tab:PF_parameter}%
  Poole-Frenkel parameters $\mu_0$ (in $\unit[]{cm^2/(Vs)}$) and $\beta$ (in $\unit[]{\sqrt{cm/V}}$) of the multiscale modeled MADN, calculated by the six different HFX values. 
  }
  \begin{ruledtabular}
    \begin{tabular}{c c c}
    $\ahfx$ & $\mu_0$  & $\beta$ \\
      \hline
    0 & $4.0 \cdot 10^{-3}$ & $1.0 \cdot 10^{-3}$ \\
    0.05 & $2.1 \cdot 10^{-3}$ & $9.3 \cdot 10^{-4}$ \\
    0.10 & $1.0 \cdot 10^{-3}$ & $1.5 \cdot 10^{-3}$ \\
    0.15 & $8.0 \cdot 10^{-4}$ & $1.6 \cdot 10^{-3}$ \\
    0.20 & $9.3 \cdot 10^{-4}$ & $1.3 \cdot 10^{-3}$ \\
    0.25 & $2.6 \cdot 10^{-4}$ & $1.8 \cdot 10^{-3}$ \\
      \end{tabular}
  \end{ruledtabular}
  \end{table}

Figure~\ref{fig:PF_plot_ave} shows the plot of the charge mobility one logarithmic $y$-axis as a function of $\sqrt{F}$ to reveal the electric field dependence of the type $\mu(F)=\mu_0 \exp (\beta \sqrt{F})$ as predicted by Poole and Frenkel~\cite{frenkel_prebreakdown_1938}. We show the explicit results for the six chosen \ahfx values together with the confidence interval estimate from the uncertainty quantification via Monte-Carlo sampling. In Table~\ref{tab:PF_parameter} we also summarize the  parameters $\mu_0$ and $\beta$ extracted from fits of the explicit data to the Poole--Frenkel expression. The values for $\mu_0$ vary from $\unit[2.6\cdot 10^{-4}]{cm^2/(Vs)}$ to $\unit[4.0\cdot 10^{-3}]{cm^2/(Vs)}$, roughly one order or magnitude depending on the chosen \ahfx, in line with the uncertainty from the Monte-Carlo sampling. The Poole--Frenkel slope $\beta$ in contrast is found to be much less sensitive to uncertainties, with recorded values between $\unit[9.3\cdot 10^{-4}]{\sqrt{cm/V}}$ and $\unit[1.8\cdot 10^{-3}]{\sqrt{cm/V}}$.

\bjoern{STOP}{HERE}
\begin{itemize}
\item \ahfx, while only a proxy for the use of different functionals in MMM, gives a good indication the challenges in obtaining quantutative predictions of charge mobilities
\item uncertainty for a low/moderate disorder material covering a range of one order of magnitude 
\item field-dependence much less affected
\item uncertainty mostly stems from site energy uncertainties, in a broader sense this highlights the importance for accurate methods to determine these energies not just as a distribution
\end{itemize}
